``Order is Half of Life'' -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved Efficiently)

### 2022-12-23 paper/paper-mainfile.tex
diagram

			\action{Add}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{Prec}{SinglePrec,
			width  = 2.5em, 
			height = 2.5em, 
			pre length = 1em,
			eff length = 1em,
			body = {left = 4em of Add} 
			};

			\action{Del}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of Prec} 
			};

@@

			\action{A}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of first} 		
			};

			\action{C}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of second} 	
				%body = {below left = 2em and 2em of } 
			};

@@

	\scalebox{0.75}{
		\begin{subfigure}{6cm} 
		 %	\centering
			\caption{Delete any random ordering to break it}
			\label{fig:CycleBreaking2}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

>>>>

			\action{Prec}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{Del}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of Add} 
			};

@@

			\action{A}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of B}	
			};

			\action{C}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of A} 
			};

@@

	\vspace{2em}
	\scalebox{0.75}{
		\begin{subfigure}{7cm} 
		 %	\centering
			\caption{Delete any random ordering to break it}
			\label{fig:CycleBreaking2}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
